---
output: github_document
bibliography: LATER.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LATERmodel

<!-- badges: start -->
[![R-CMD-check](https://github.com/unimelbmdap/LATERmodel/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/unimelbmdap/LATERmodel/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The LATERmodel R package is an open-source implementation of Roger Carpenter's 
Linear Approach to Threshold with Ergodic Rate (LATER) model 
(@carpenter_eye_1981, @noorani_later_2016). This package enables the easy 
visualisation of reaction time data in LATER's signature reciprobit space, as 
well as estimating parameters to fit the model to datasets, comparing raw 
datasets, comparing fits (i.e., is the dataset better explained by a shift or a 
swivel?), adding an early component, etc.

This package also includes two canonical datasets digitised from 
@carpenter_neural_1995 and @reddi_accuracy_2003.

## Installation

You can install LATERmodel with:

``` r
install.packages("LATERmodel")
```

## Example

Load digitised data from Figure 1 in Carpenter and Williams (1995):

```{r example}
library(LATERmodel)

data(carpenter_williams_1995)
```

Extract data corresponding only to participant `a` (Figure 1.a):

```{r}
raw_data <- subset(carpenter_williams_1995, participant == "a")
```

The data analysis functions within this package require the raw data to first 
undergo pre-processing using the `prepare_data` function.
We pass our `raw_data` variable as the argument to the `raw_data` parameter 
of `prepare_data` to perform such pre-processing:

```{r}
data <- prepare_data(raw_data = raw_data)
```


Fit each condition individually (no shared parameters between them), and 
include an early component for all of them:

```{r}
data_fit <- individual_later_fit(data, with_early_component = TRUE)
```

Visualise the raw data and the best individual fits:

```{r}
reciprobit_plot(data, data_fit)
```

For a more detailed analysis using the `LATERmodel` R package, see [this article](https://unimelbmdap.github.io/LATERmodel/articles/cw1995_analysis.html).
